%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MASTER'S THESIS                                                            %%
%%                                                                            %% 
%% Title (en): Mining Parallel Corpora from the Web                           %%
%% Title (sk): Rafinácia paralelných korpusov z webu                          %%
%%                                                                            %%
%% Author: Bc. Jakub Kúdela                                                   %%
%% Supervisor: Doc. RNDr. Irena Holubová, Ph.D.                               %%
%% Consultant: RNDr. Ondřej Bojar, Ph.D.                                      %%
%%                                                                            %%
%% Academic year: 2015/2016                                                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

First, I would like to thank my supervisor Doc. RNDr. Irena Holubová, Ph.D. for inspiring me when selecting the topic related to my interests, for her valuable and professional advice, and for the time she has spent helping me with the thesis. I would also like to express my gratitude to my consultant RNDr. Ondřej Bojar, Ph.D. for introducing me to the domain of natural language processing and for his time and ideas, which helped me a lot. I am very greatful to my parents Libuša and Ivan for their determination to support me as much as possible. Next, I would like to thank my brother Lukáš, who has always motivated me as a great older sibling. Last but not least, I am thankful to my sweetheart Zuzana for her patience and everything she does for me. 

Once again, thank you!

% Temporarily select the Slovak language (with French spacing).
\selectlanguage{slovak}
\frenchspacing
\vspace{1em}

V prvom rade chcem poďakovať mojej vedúcej Doc. RNDr. Irene Holubovej, Ph.D. za inšpiráciu pri výbere témy blízkej mojím záujmom, za jej cenné a odborné rady, ochotu a čas ktorý mi v priebehu písania práce venovala. Rovnako by som rád poďakoval môjmu konzultantovi RNDr. Ondřejovi Bojarovi, Ph.D. za uvedenie do problémov domény spracovania prirodzeného jazyka, za jeho čas a nanápady, ktoré mi v práci nesmierne pomohli. Velká vďaka patrí mojim rodičom Libuši a Ivanovi za ich velké odhodlanie podporiť ma v živote najviac ako sa len dá. Taktiež chcem poďakovať svojmu bratovi Lukášovi, ktorý ma vždy v mnohom motivoval ako skvelý starší súrodenec. V neposlednom rade ďakujem mojej priateľke Zuzane, za jej trpezlivosť a za všetko čo pre mňa robí.

Ešte raz Vám všetkým ďakujem!

% Returning to the English language (disabling French spacing).
\selectlanguage{english}
\nonfrenchspacing
